\documentclass[11pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}


% Custom section command
\titleformat{\section}
  {\large\bfseries\uppercase}
  {}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{*1.5}{*0.5}

% Remove page numbers
\pagenumbering{gobble}

% Custom commands
\newcommand{\name}[1]{
  \begin{center}
    \Huge\textbf{\href{https://rb.gy/qco3w0}{#1}}
  \end{center}
  
}
\newcommand{\contact}[3]{
  \begin{center}
    #1 \\
    #2 \\
    #3
  \end{center}
  % \vspace{-0.5em}
  % \hrule height 0.4pt width \textwidth
  \vspace{0.5em}
}
\newcommand{\role}[4]{
  \begin{center}
  \textbf{#1} \hfill \textbf{#2} \\
  \textit{#3} \hfill \textit{#4}
}

\begin{document}

\name{Harsh Shukla}
\contact{+(91) 9839182940 | India | Shuklax@proton.me | \href{https://www.linkedin.com/in/shuklax/}{\faLinkedin\hspace{0.5em} Shuklax} | \href{https://github.com/Shuklax}{\faGithub\hspace{0.5em} Shuklax}}


\section{PROFESSIONAL EXPERIENCE}

\vspace{1em}
\role{BillionByte Technologies}{Mumbai, India}{Software Developer – Focus on Infrastructure & DevOps}{June 2023--Present}
\begin{itemize}[leftmargin=*,nosep]
  \item Spearheaded and maintained production-grade codebases across multiple client and internal projects, delivering features end-to-end in a high-velocity, service-to-product transition environment.
  \item Monitored system health and deployment logs, contributed to infra debugging and incident resolution using tools like AWS CloudWatch and Docker logs.
  \item Engineered the backend of a real-time trading system with Node.js, Express, Redis (Pub/Sub), and WebSockets, capable of handling thousands of events per second with high reliability.
  \item Leveraged advanced TypeScript patterns and clean MVC architecture to build modular backend services—boosting maintainability and reducing technical debt by over 40\% across teams.
  \item Designed event-driven architectures with serverless functions, message queues, and Kubernetes (lightweight workloads), enabling scalable real-time data pipelines.
  \item Managed cloud-native deployments using Docker (multi-container setup), AWS EC2/S3, and GitHub Actions, ensuring reliable CI/CD workflows and smooth production rollouts.
  \item Mentored and onboarded new interns by breaking down complex systems into approachable components, creating documentation and walkthroughs that helped them become productive contributors within their first week.
\end{itemize}

\role{KnowledgeGATE Eduventures}{Gaziabad, India}{Mentor and Network Security Faculty}{March 2022--Jan 2023}
\begin{itemize}[leftmargin=*,nosep,topsep=0pt]
  \item Taught Network Security fundamentals and hands-on modules as a subject faculty, simplifying complex topics for undergraduate and early-career engineers.
  \item Received a personal recommendation from the COO for excellence in teaching, impact-driven mentorship, and consistent learner engagement.
\end{itemize}
  
\end{itemize}

\vspace{1em}
\section{OPEN-SOURCE}

\vspace{1em}
\role{humanize-this}{\href{https://github.com/Shuklax/humanize-this}{Github}, \href{https://www.npmjs.com/package/humanize-this}{NPM}}{}{}
\begin{itemize}[leftmargin=*,nosep]
  \item A lightweight yet powerful utility package designed to convert raw, machine-readable data into clean, human-friendly formats—optimized for real-world applications at scale. 
  \item Born out of the recurring friction experienced while working on production-grade codebases, humanize-this emerged as a modular, zero-dependency solution that simplifies the complexity of formatting numbers, time, currencies, file sizes, and text—all with full TypeScript support.
  \item 40+ stars on GitHub
\end{itemize}

% \role{PrimeGPT}{\href{https://github.com/Shuklax/PrimeGPT}{Github}}{}{}
% \begin{itemize}[leftmargin=*,nosep,topsep=0pt]
%   \item A hybrid movie platform with AI based movie recommendation system built using OpenAI API and TMDB.
%   \item Implemented Auth flow using Google Firebase, Redux toolkit for maintaining the store, Tailwind for styling resulting in a picture perfect UI/UX.
% \end{itemize}


\vspace{1em}
\section{EDUCATION}

\vspace{0.5em}
\role{DIT University}{Dehradun, India}{B.Tech in Computer Science (Specialization in Cyber Security and forensics)}{May 2021}

\vspace{1em}
\section{SKILLS}

\vspace{0.5em}
\begin{itemize}[leftmargin=*,nosep]
  \item \textbf{Languages:}  TypeScript, JavaScript, Java, HTML5, CSS3
  \item \textbf{Frontend:} React.js, Tailwind, Vite, Parcel
  \item \textbf{Backend:} Node.js, Express.js, Prisma, Mongoose
  \item \textbf{DevOps & Infra} AWS (EC2, S3, CloudWatch), GitHub Actions, Docker (multi-container orchestration), Serverless (Lambda), Kubernetes (basic workloads), Redis Streams, Message Queues, CI/CD
\end{itemize}

\end{document}
